\documentclass[10pt, letterpaper]{article}

\input{preamble}

\begin{document}
\pagestyle{empty}

\input{header}

\vspace{0.5cm}

\begin{center}
{\large \textbf{Cover Letter --- Backend Developer at Akselos}}
\end{center}

\vspace{0.3cm}

\begin{onecolentry}

April 15, 2026

\vspace{0.3cm}

Dear Hiring Team at Akselos,

\vspace{0.2cm}

I am writing to express my strong interest in the \textbf{Backend Developer} position at Akselos. With over 3 years of professional experience spanning backend development, cloud infrastructure, and systems engineering, I am excited about the opportunity to contribute to a platform that powers safety-critical decisions for industrial assets.

\vspace{0.2cm}

\textbf{Why I'm a strong fit:}

\vspace{0.1cm}

In my current role at \textbf{MobiFone Telecommunications Corporation}, I develop and maintain mission-critical systems --- including the Smart OTP authentication platform and data analytics pipelines built with Python (Pandas, Streamlit). I design backend services and APIs powering internal dashboards, and work daily with SQL databases (Oracle, PostgreSQL) for telecom network performance analysis. Working in a telecom environment has instilled a deep appreciation for system reliability, security, and operational discipline --- values I understand are equally central to Akselos's SPM platform.

\vspace{0.2cm}

Previously at \textbf{ActsOne}, I designed and operated end-to-end infrastructure platforms, including Kubernetes clusters, database replication systems (MySQL/PostgreSQL), and distributed backend services built with Golang and gRPC. I architected CI/CD pipelines, implemented Infrastructure as Code with Ansible, and built zero-trust security architectures --- all skills directly applicable to maintaining and scaling Akselos's cloud and on-premise deployments.

\vspace{0.2cm}

\textbf{What excites me about Akselos:}

\vspace{0.1cm}

The challenge of building backend systems that support complex simulation workflows and high-performance computing at industrial scale is exactly the kind of work I find most rewarding. My experience bridging the gap between infrastructure and application development --- from provisioning servers to designing APIs --- positions me well to contribute across the full stack of your backend operations.

\vspace{0.2cm}

I am proficient in Python and SQL, experienced with Linux systems administration, and comfortable working with distributed systems and cloud platforms. My frontend experience with React and Next.js also allows me to contribute to UI improvements when needed.

\vspace{0.2cm}

I would welcome the opportunity to discuss how my experience in building reliable, secure backend systems can contribute to Akselos's mission. Thank you for your consideration.

\vspace{0.5cm}

Best regards,\\
\textbf{Pham Huy Thanh}

\end{onecolentry}

\end{document}
